\documentclass[12pt, oneside]{article}
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper} 
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{float}
\usepackage{subfig}
\usepackage[flushleft]{threeparttable}
\usepackage{gensymb}
\usepackage{multirow}
\usepackage[dvipsnames]{xcolor}
\newcommand{\BibTeX}{\textsc{Bib}\TeX}
%opening
\title{list}
\author{}

\begin{document}
\maketitle
% \tableofcontents

\section{} 
dnsmst\_utilities/src/serial/Average/

add parallel version for time average code

\section{}
dnsmst\_utilities/src/serial/Postprocessing/volume/volume\_HDF5/

add parallel version for volume code

\section{}
dnsmst\_utilities/src/serial/Postprocessing/p3d2HDF5/

add parallel version for the format conversion code

\section{}
Virtual Dataset (VDS) HDF5

Create virtual dataset using HDF5 format

\section{}
Compressed Dataset HDF5

Create compressed dataset using HDF5 format

\section{}
dnsmst\_utilities/src/serial/common/modRWHDF5.f90

Create module file to read and write HDF5 data using Matlab

\section{}
PDF (probability density function) of wall pressure fluctuation.

Reference: Tsuji et al.~\cite{tsuji2007pressure}

\section{}
Add bottom BC reading 4 k-plane timeseries data.

1) Generate the 4-iplane or 4-kplane timeseries data.

In deck3d.inp, turn on PlaneseriesSave, the file modSaveInflowPlanes.f90 will generate the 4-iplane data or 4-kplane data. Please check the output data.    

2) Read the 4-iplane timeseries data.

In deck3d.inp, set inletbc=1 and inletdatatype=3, the file planeinlet.inp should also be provided. 


Please check the following case for how to read the 4-iplane timeseries data.
/share/duan/czb58/test\_DNS/Test\_cases/Test\_ShockNoise\_2016-10-10\_largeZ\_4p5/

\newpage

\bibliography{ref}
\bibliographystyle{aiaa}


\end{document}
